An open reproducible framework for the study of the iterated prisoner's dilemma

### 2015-11-25 tex/paper.tex

>>>>

Ideas for this section:
* ZD strategies -- extortionate strategies win well but no ZDs score partiocualrly well,
even ZDGTFT2. With noise the ZD strategies don't win well either.
* TFT, T2FT, TF2T -- no so great but variants with e.g. deadlock breaking, such as OmegaTFT,
fare well
* It's posible to win many matchups as well score highly -- backstabber, doublecrosser,
foolmeonce. These strategies also score well in noisy tournaments
* It's possible to be generally cooperative and still exploit naive strategies effective,
such as LookerUp and MetaHunter
* Long memory strategies are generally better
* Meta strategies fare very well in general, also in noisy tournaments
* Variance of score distributions is surprisingly low

Plot of memory_depth vs mean score, mean wins?
